Biodiversity temporal trends are reshaping food web structure and redundancy in riverine ecosystems

### 2025-04-17 paper/appendix.Rmd

```{r}
tar_load(c(op_table, com_metric_tab))
tab_quanti <- purrr::map_dfr(
  list(com_metric_tab, op_table),
  function(x) {colnames(x)[1] <- "Variable"; x}
)
tab_quanti %>%
  kbl(
    caption = "Summary distribution of community metrics and fish monitoring variables.",
    booktabs = T
    ) %>%
  kable_styling() %>%
  pack_rows("Community metrics", 1, 8) %>%
  pack_rows("Summary of fish monitoring", 9, 13)
```

>>>>

```{r}
tar_load(c(op_table, com_metric_tab))
tab_quanti <- purrr::map_dfr(
  list(com_metric_tab, op_table),
  function(x) {colnames(x)[1] <- "Variable"; x}
)
tab_quanti %>%
  kbl(
    caption = "Summary distribution of community metrics and fish monitoring
    variables. Q1 and Q3 are the first and third quartiles of the
    distributions.",
    booktabs = T
    ) %>%
  kable_styling() %>%
  pack_rows("Community metrics", 1, 8) %>%
  pack_rows("Summary of fish monitoring", 9, 13)
```
